Innovative Technologies for and Observational Studies of Star and Planet Formation

### 2015-04-14 gullydiss.tex
add content to the Acknowledgments, refactor a bit

MGS acknowledges support from the NASA Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA APRA grant NNX10AC68G, NASA ACT grant NNX12AC31G, and NSF ATI grant AST-0705064.  MGS acknowledges support from the University of Texas in the form of the Graduate Dean's Prestigious Fellowship.  Funding from the McDonald Observatory and the Department of Astronomy's Cox graduate student excellence funds have helped to support travel and other aspects of this research.  Portions of this work were supported by the NASA Origins grant number NNX07AI83G.

Part of the research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.

Some of the JWST work was carried out at the University of Texas under a contract from the University of Arizona.  The development work for the grisms was supported in part by NASA (grant number NNX07AV15H).  Analysis of the silicon antireflection coatings was supported in part by grant 0705064 from the National Science Foundation.  The authors wish to thank Gary Poczulp and the National Optical Astronomy Observatory for assistance in producing the interferograms presented in this paper.

I would like to thank student colleages Dr. Jasmina Marsh, Dr. Casey Deen, Jared Rand, Amanda Turbyfill, Carleen Boyer, for direct involvement in portions of this work.

>>>>

This work would not have been possible without the mentorship of my collaborators Katelyn Allers and Alycia Weinberger, for which I am deeply indebted.  I acknowledge the mentorship and patience of my former student colleagues Dr. Jasmina Marsh and Dr. Casey Deen.  I am grateful for the efforts of my junior colleagues Jared Rand, Amanda Turbyfill, and Carleen Boyer for their contributions to the Silicon Diffractive Optics Group.  Engineers Weisong Wang and Cindy Brooks contributed substantially to the Si diffractive optics fabrication.  I am indebted to my NASA GRSP mentor Daniel Wilson, with whom it was a pleasure to work.  I am thankful for the supervision of Richard Muller and Victor White at the Microdevices Laboratory.

I am delighted to acknowledge support from the NASA Graduate Student Research Program (GSRP) Fellowship, grant NNX10AK82H.  Portions of this research were supported by NASA APRA grant NNX10AC68G, NASA ACT grant NNX12AC31G, NSF ATI grant AST-0705064, and NASA Origins grant number NNX07AI83G.  MGS acknowledges support from the University of Texas in the form of the Graduate Dean's Prestigious Fellowship and from the Department of Astronomy in the form of the David Benfield Memorial Fellowship in Astronomy.  Funding from the McDonald Observatory and the Department of Astronomy's Cox graduate student excellence funds have helped to support travel and other aspects of this research.  Part of the research was carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.  Some of the work in Chapter \ref{chSPIE_2010_JWST} was carried out at the University of Texas under a contract from the University of Arizona.  The development work for the grisms was supported in part by NASA (grant number NNX07AV15H).  The authors wish to thank Gary Poczulp and the National Optical Astronomy Observatory for assistance in producing the interferograms presented in Chapter \ref{chSPIE_2010_JWST}.  This dissertation includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observatory, Chile.

%I was lucky to be part of such a talented and creative group of incoming graduate students.  Thank you to all the friendly, funny, and courageous people of Austin I met along the way---too numerous to identify---for contributing to my prosperity here.  And of course thank you to my family and friends.

A very special thank you is reserved for my advisor, Daniel Jaffe, for contributing so deeply to my professional growth.  In particular I acknowledge his guidance in writing the dissertation you see here, and entertaining some of my crazy ideas.
